The Intersection Operator Diagram
English: Visually confirms Axiom 4. Spacetime is not an empty box; it is a scanning hyperplane slicing through a higher-dimensional rigid knot. The points where the line breaks through the glass are what a macroscopic observer interprets as "matter."  
Русский: Наглядно подтверждает Аксиому 4. Пространство-время — это не пустая коробка, а сканирующая гиперплоскость, рассекающая многомерный жесткий узел. Точки, где линия пронзает плоскость среза, макроскопический наблюдатель интерпретирует как «материю».  
2. Jordan Canonical Phase Portrait
English: Visually proves Section 3.1. Trajectories flow cleanly down the degenerate eigenvector stream without orbiting or overshooting, demonstrating how critical damping protects system values from singular degradation during dimensional shifts.  
Русский: Визуально доказывает Раздел 3.1. Траектории чисто стекают по вырожденному собственному вектору без вращения или проскока, демонстрируя, как критическое затухание защищает системные ценности от сингулярной деградации при мерностных сдвигах.  
3. Lemniscate Shear Deficit Layout
English: Establishes the precise physical boundary conditions where \delta_{\text{shear}} \approx 0.681690 prevents coordinate collapse. It shows the localized state transfer point where states transition without causing a singular tearing of the underlying metric field (\det(g_{\mu\nu}) \neq 0).  
Русский: Фиксирует точные физические граничные условия, при которых \delta_{\text{shear}} \approx 0.681690 предотвращает коллапс координат. Показана локализованная точка передачи, где состояния переходят без сингулярного разрыва базового метрического поля (\det(g_{\mu\nu}) \neq 0).  
